### 2012-08-02 docs/MESA/instructions.tex
add footnote

Modules for Experiments in Stellar Astrophysics ({\tt MESA}) is a collection 
of open source, robust and efficient modules developed for a wide range of 
applications in computational stellar astrophysics. The modules include 
macroscopic and microscopic physics such as nuclear reaction rates, opacity, 
equation of state, element diffusion data and atmosphere boundary conditions 
in addition to numerical routines. This document describes how to link the 
{\tt MESA} modules to an outside program such as {\tt MAESTRO}.

>>>>

Modules for Experiments in Stellar Astrophysics ({\tt MESA}) is a
collection of open source, robust and efficient modules developed for
a wide range of applications in computational stellar
astrophysics. The modules include macroscopic and microscopic physics
such as nuclear reaction rates, opacity, equation of state, element
diffusion data and atmosphere boundary conditions in addition to
numerical routines. This document describes how to link the {\tt MESA}
modules to an outside program such as {\tt MAESTRO}\footnote{This
  interface work was done by Ryan Orvedahl---questions (and credit)
  should be directed to him}.
